Title?

### 2019-09-26 Old/April/paper_alphafair.tex
Work

\usepackage{multicol}
\usepackage{url}

@@

\section{Abstract}

We investigate the 2cm app, a data-exchange platform published for China Mobile Hong
Kong 4G Pro Service Plan customers. Telecommunications providers' revenue is typically
gained by charging users a fixed fee for a maximum amount
of data usage in a month, i.e., a monthly data cap \cite{???}. 
2cm's (2nd exchange market) data exchange platform allows users to submit
bids to buy and sell data.
This usage model, is, as far as our knowledge, the first data trading
platform that allows customers to buy and sell their own data.
We describe a distributed auction mechanism for data exchange inspired by the
classic PSP throughput problem,
and prove that our distributed data exchange mechanism provides incentive
compatibility (social choice function), and that we have efficiency
using only partial valuation information of each participant in an exchange market.

In applying a distributed PSP implementation to CMHK's secondary market, we
find that
the market is able to achieve an equilibrium as the sellers and buyers have an
incentive for a collaborative exchange, and design our mechanism tp provide the functions
for effective communication between the connected users. We claim that in
this secondary market our formulation holds the desired VCG qualities through the construction of a
probable equilibrium \cite{???}. We further provide bounds on the auction duration, 
with respect to the classic throughput problem.
and provide simulated results on convergence time to support our (FIND
COMPETITVE RATIO!), and a bound
on the convergence of our mechanism. We extend the works of cite!cite!
i.e. (market influence/EQ,social EQ,payment/allocation models) OR (bandwidth, data bundles, distributed
market algorithms) and show the existence of a dynamic global market equilibrium, allowing for a unique set of market dynamics.

\section{Introduction}

In this work, we propose \emph{a distributed progressive second price (PSP) auction in
order to maximize social utility in this secondary market}. Using the
distributed PSP mechanism on CMHKs data
exhange platform, we show that for cellular data allocated between multiple users there
exists an $\epsilon$-Nash market equilibria. A quality of the PSP auction is that
demand information is not known centrally, rather, it is distributed in the
buyers' valuations. The mechanism for an auction is defined
as \emph{distributed} when the allocations at any element depend only on
\emph{local} state: the quantity offered by the seller at that element, and the
bids for that element only \cite{lazar}. In this work, the proposed mechanism
allows the distribution of bids, where there are many providers each holding
thier own local auction; there is no entity that holds a global market knowledge.

In a PSP mechanism, bids consist of (i) an available (required) quantity and (ii) a unit-price (calculated
using its own demand functions). Buyers submit bids cyclically until an
($\epsilon$-Nash) equilibrium is reached and a local auction is concluded.

(FEE IS FIXED OR
PER-UNIT?)(HOW DO WE MODEL ISP REVENUE? IMMEDIATE FUTURE)

@@

\subsubsection{Allocation using PSP}

We begin with a brief introduction to the generalized distributed PSP auction, first introduced by Lazar and Semret \cite{lazar}.
We define a set of $\mcI = \lbrace 1,\cdots,I\rbrace$ users.

Suppose each user $i \in \mcI$ makes a bid $s_i^j = (p_i^j, d_i^j)$ to the
seller of resource $j$, where $p_i^j$ is the unit-price the user is willing to
pay and $d_i^j$ is the quantity the user desires. The \emph{bidding profile} forms a grid, $s \equiv
[s_i^j] \in \mcI \times \mcI$, and $s_{-i} \equiv [s_1^j , \cdots , s_{i−1}^j , s_{i+1}^j , \cdots
, s_I^j]_{j\in\mcI}$ is the profile of user $i$'s opponents.

Using this classic PSP mechanism, \cite{lazar} shows that given the opponents
bids $s_{-i}$,
user $i$'s $\epsilon$-best response $s_i = (w_i, v_i)$ as a Nash move
where $\epsilon > 0$ is the bid fee, $b_i$ is user $i$'s budget, and every user
has an elastic demand function.

Based on the profile of bids $s^j = (s^j_1, \cdots s^j_I)$, there exists
an allocation $(a^j, c^j) = A^j(s^j)$, where $a^j_i$ is the quantity given to
each user $i\in\mcI$ and $c^j_i$ is the total cost charged to user $i$. $A^j$ is the
allocation rule of seller $j$. It is feasible if $a^j_i \le d_i^j$, and $c^j_i \le  p^j_i d_i^j$.

We intend to show that our auction
is rational and achieves the desired VCG properties, as does the original
formulation. Using \cite{zheng} as a basis for our model, and \cite{lazar} as
realistic, theoretic, and notational templates, we define optimal strategies for
CMHK users, and demonstrate that the development of a set PSP auction mechanisms
in a data exchange setting is able achieve a network equilibrium for cellular data.

We intend to show that our PSP constraints are
sufficient to attain the desirable property of truthfullness through incentive compatibility. We
reason, due to our pricing mechanism, that our formulation upholds the \emph{exclusion-compensation
principle}, and is a valid progressive second price auction to the extent that buyer $i$
pays for its allocation so as to exactly cover the ``social opportunity cost"
which is given by the declared willingness to pay (bids) of the users who are
excluded by $i$'s presence, and thus also compensates the seller for the maximum lost potential
revenue \cite{lazar}.

We will introduce a user type called an \emph{opt-out buyer} in order to perform our analysis. The
opt-out buyer restricts its pool of sellers. We extend the P2P rules described
in \cite{semret} to account for a set of \emph{local} data-exchange markets.
Our reserve price function is determined by the subset of nodes participating in the
auction, where the seller is its own auctioneer. This implies that the influence of the greater market on the individual
auctions will be influenced only by the submission of bids from buyers to
sellers. As a buyer may have access to multiple auctions, the sellers will be
dynamically influenced by the market via the $\epsilon$-best replies from the
buyers. We demonstrate that as the valuation function of seller $j$ is dependent
on the buyers demand, that the strategies of buyers and sellers may differ
drastically depending on the market.

@@

We define the set of users, $\mcI = \lbrace 1, \cdots, I\rbrace$, who purchase or sell
data from other users. A buyer submits bids directly to sellers, where we
assume that all users submit bids in order to maximize their
(private) valuation functions.

(TERRIBLE, FUTURE WORK) public information in the
secondary market consists of a set of offers that are published by users
wishing to sell their data overage.

A user's identity $i \in \mcI$ as a subscript indicates that the user
is a buyer, and a superscript indicates the seller.
Suppose user $i$ is buying from user $j$. A bid $s_i^j = (d_i^j, p_i^j)$,
meaning $i$ would like to buy from $j$ a quantity $d^j_i$ and is willing to pay
a unit price $p^j_i$. Without loss of generality, we assume that all users bid in all
auctions; if a user $i$ does not submit a bid to $j$, then this means that
the user has the exact amout of data they require, or that seller $j$ does not have
enough data to satisfy the buyers demand, and we simply set $s_i^j = (0, 0)$.
A seller $j$ places an ask $s^j = (d^j, p^j)$, meaning $j$ is offering a
quantity $d^j$ , with a reserve unit price of $p^j$ . In other words, for a
superscript, the bid is understood as an offer in the secondary
market; we assume that data is a unary resource belonging to the seller, and
therefore can identify the data (for sale) with the identity of the user.
To further clarify this restriction, we note that since $i$ is not a seller,
the superscript notation will not be used, as $d^i = 0$ and
$a^i = 0$. In our current formulation, we do not allow a seller to submit
multiple bids to the secondary market (FUTURE WORK).

\section{Distributed PSP Analysis}

\subsection{User Behavior}

We assume that users are selfish, and therefore
rational. Users prefer to participate in the secondary market as it allows them to purchase
additional data for a cost less than the overage fee set by the ISP. 
User preferences are defined by a utility function, for any $i\in\mcI$,
\begin{align*}
    u_i : &S \rightarrow (-\infty, \infty) \\
          &s \rightarrow u_i(s).
\end{align*}
(TOO GENERAL?)

\subsubsection{Buyer Strategy}

Absent the cost or revenue from trading data, CMHK users gain utility from consuming
data. 
We will assume that the buyer valuation satisfies the conditions for an
\emph{elastic demand function}: 
\definition{\cite{lazar}}
A real valued function, $\theta(\cdot)_i$, is an \emph{(elastic) valuation
function} on $[0, D]$ if 
\begin{itemize}
    \item $\theta_i(0) = 0$,
    \item $\theta_i$ is differentiable,
    \item ${\theta_i}' \ge 0$, and ${\theta_i}'$ is non-increasing and continuous,
     \item There exists $\gamma > 0$, such that for all $z \in [0,D]$,
${\theta_i}'(z) > 0$ implies that for all $\eta \in [0, z), {\theta_i}'(z) \le
{\theta_i}'(\eta)
- \gamma(z - \eta)$. 
\end{itemize}

% OPT-OUT BUYER
We define a \textbf{opt-out buyer} as a user $i\in\mcI$ with utility
function,
\begin{equation}\label{buyerutility}
    u_i = \theta_i \circ e_i(a) - c_i,
\end{equation}
where $e_i : [0, \infty) \rightarrow [0,\infty)$ is %the expectation 
a function that maps buyer $i$'s data quantity (requirement) to matching
seller(s). We note that the opt-out buyers valuation depends only on a scalar $e_i(a)$ which is a function of the
quantities of all the available data for sale in the secondary market.

Suppose the total amount of seller $j$'s data on the network at the instance that
user $i$ joins the auction is $b^j$. 
A sellers' allocation cannot exceed the total amount they have available,
i.e. $a_i^j \le b^j$. This will hold simultaneously for each $i \in
\mcI$ if and only if $b^j \ge \max_i \ a_i^j$. Therefore a seller $j$ is
restricted to subset of buyers $\in\mcI$.
Note that with our formulation, if a seller $j$ does not meet a buyer $i$'s data requirements, a
rational (utility-maximizing) buyer will set $s_i^j = 0$. The seller, in our analysis, is a functional
extension of the buyer, with valuation $\theta^j$ constructed by buyer demand.
We assume that buyers and sellers are separated (a seller does not also buy
data and vice versa).

Although it is possible for a seller to fully satisfy a buyer $i$'s demand, it
is also reasonable to expect that a seller may come close to using their
entire data cap, and only sell the fractional overage. In this case, we
determine that a buyer must coordinate their bids among multiple sellers. 
Buyer $i$'s valuation is interpreted as a unit valuation $\theta_i$,
moderated by the function $e$ which maps its data requirement to the distributed market. 
We propose the following strategy,
{
\proposition{(Opt-out buyer strategy)}\label{buyerstrategy}
Let $i\in\mcI$ be a buyer and define any auction duration
to be $\tau \in [0,\infty)$, and fix all other buyers' bids $s_{-i}$. 
For any allocation $a$, let
% OPT-OUT BUYER STRATEGY
\begin{equation}\label{opt-out}
    %e_i^j(a) \triangleq \frac{a_i^j}{\vs_i^j} 
    e_i^j(a) \triangleq a_i^j,
\end{equation}
and define,
% MIN SET
$$
    \ell_i =\argmax_{\mcI' \subset \mcI, \vert\mcI'\vert =
n}\sum_{j\in\mcI'} d^j.
$$
Buyer $i$ chooses its seller pool by determining $n$, where
\begin{equation}\label{buyercoordinate}
    %n = \argmin_{\ell_i}(j \in \ell_i : \displaystyle\sum_{n} \frac{d^n}{d_i}
    n = \argmin_{\ell_i}(j \in \ell_i : \displaystyle\sum_{n} d^n
\ge d_i\rbrace,
\end{equation} 
which produces a minimal subset 
\begin{equation}\label{sellers}
    \mcI_i = \lbrace j \in \mcI : j \le n\rbrace \subset \mcI.
\end{equation} 
Now let $j^* = n \le I$, and define, 
\begin{equation}\label{opt-minallocation}
    e_i(a) \triangleq e_i^{j^*}(a).
\end{equation}
we address the following special cases:\\
(Budget limited allocation)
\begin{equation}\label{partialallocation}
    d_i^j > b^j - \sum_{k\in\mcI^j, k\ne i} d_k^j.
\end{equation}
(Equal price allocation)
There exists $k,i \in \mcI^j, k\ne i$, such that
\begin{equation}\label{equalprice}
    \quad p_i^j = p_k^j.
\end{equation}
(Price-dominant allocation)
There exists $k \ni \mcI^j$, where $\forall \ i\ne k \in \mcI^j$.
\begin{equation}\label{newbuyer}
    p_k^j < p_i^j, 
    %p_i^j < p_k^j \quad \text{and} \quad d_i^j >= b^j, \quad \forall \ k \in \mcI^j.
\end{equation}
(Empty allocation)
\begin{equation}\label{emptyset}
    n > \vert \mcI\vert \Rightarrow \ell^j = \emptyset.
\end{equation}
In any of the above cases, seller $j$'s local auction strategy does not change and
Proposition \ref{sellerstrategy} holds.
Then, we have that $e_i$
is an optimal feasible strategy for buyer $i$.
}\\
\textbf{Proof:}
In the case that there exists a seller who can completely satisfy a buyers'
demand, $j^*=1$, $\vert \mcI_i\vert =1$ and (\ref{buyercoordinate}) holds. If such a buyer does not exist,
as the set $\ell_i$ is an ordered set, $i$ may discover 
$j^*$ by computing $\ell_i$. In the case that $d_i >
\sum_{j\in\mcI}d^j$, then $j^* > I$, we reason that this case is unlikely; our formulation reduces to a
monopoly, and the user pays the overage fee for data set by the provider which the upper bound of the sellers'
pricing function, where we consider the provider (AT\&T) as a seller. We also note that $\mcI_i$ is not the only
possible minimum subset $\in\mcI$ able to satisfy $i$'s demand, it is the
minimal ordered subset where a
coordinated bid is possible, which we will address in further analysis in Section \ref{analysis}.
Suppose there exists buyer $k\in \mcI^j$, such that
$e_k^j(a) \ge e_i^j(a)
\rightarrow p_k^j > p_i^{j}$ and so $d^j - d_k^j < z_i^{j*}$, resulting in a
partial allocation. Bid $s_k \in S_i$, and so is considered in buyer $i$'s strategy. 
As buyer $i$ is allowed to choose subset $\mcI_i$, and $\mcI_i$ is a minimal
set, (\ref{buyercoordinate}) states that $n$ is such that $e_i(a) = e_i^{j*}(a)
\ge e_k(a)$. We assume that $i$ will faithfully follow the opt-out strategy, and
so such a buyer $k$ cannot exist. 
Now, suppose that $p_k^j = p_i^j$, however $d_k^j > d_i^j$.

>>>>

\usepackage{multicol}

@@

\section{Introduction}
China Mobile Hong Kong (CMHK) recently introduced such a secondary market.
CMHK’s 2cm (2nd exchange market) data exchange platform allows users to submit
bids to buy and sell data, with CMHK acting as a middleman both to match buyers
and sellers and to ensure that the sellers’ trading revenue and buyers’
purchased data are reflected on customers’ monthly bills. \cite{zheng}

In this work, we propose a distributed progressive second price (PSP) auction in
order to maximize social utility in this secondary data-sharing market. We show that for cellular data allocated between multiple users there
exists an $\epsilon$-Nash market equilibria when all users bid their real marginal
valuation of the mobile data offered in the secondary market described in
\cite{zheng}. A quality of the PSP auction is that
demand information is not known centrally, rather, it is distributed in the
buyers' valuations. The mechanism for an auction is defined
as \emph{distributed} when the allocations at any element depend only on
\emph{local} state: the quantity offered by the seller at that element, and the
bids for that element only. In this work, the proposed mechanism allows sellers submit bids to buyers
directly; there is no entity that holds a global market knowledge.

We suppose that each seller (resp. buyer) can submit a bid to the secondary
market consisting of (i) an available (required) quantity and (ii) a unit-price (calculated
using its own demand functions). Buyers submit bids cyclically until an
($\epsilon$-Nash) equilibrium is reached where $\epsilon$ corresponds to a bid
fee to be paid to the ISP on completion of the transaction. (FEE IS FIXED OR
PER-UNIT?)(DO WE MODEL ISP PROFIT? FUTURE WORK)

@@

\subsubsection{Bandwidth Allocation using PSP}

We begin with a brief introduction to the distributed PSP auction for the
bandwidth allocation problem, first introduced by Lazar and Semret \cite{lazar}.
The distributed PSP auction from \cite{lazar} forms a part of the
overall market based allocation model. They consider a noncooperative game
where a set of $\mcI = \lbrace 1,\cdots,I\rbrace$ users buy a fixed
amount of resource $D_i$ from a set of resources $\mcI = \lbrace 1,\cdots,L\rbrace$.

Suppose each user $i \in \mcI$ makes a bid $s_i^l = (p_i^l, d_i^l)$ to the
seller of resource $l$,
where $p_i^l$ is the unit-price the user is willing to pay and $d_i^l$ is the
quantity the user desires. The \emph{bidding profile} forms a grid, $s \equiv
[s_i^l] \in \mcI \times \mcI$ (BAD NOTATION?
SEEMS OK)  and $s_{−i}^l \equiv [s_1^l , \cdots , s_{i−1}^l , s_{i+1}^l , \cdots
, s_I^l]_{l\in\mcI}$ is
the profile of user $i$’s opponents. In addition, the user type now includes a
\emph{routing variable}, $r_i\in\lbrace 0, 1\rbrace^L$ to manage throughput in
an arbitrary collection of nodes where $r_i^l >0$ if and only if $l(i)$ is on
$i$'s path, i.e. $l(i) \in \lbrace l\in \mcI : r_i^l >0\rbrace$. 
The market now shares $L$ resources, with allocation:
$$
    \hat{D_i^l}(y,s_{-i}^l) = \bigg\lbrack D^l -
\displaystyle\sum_{p_k^l > y, k\ne i} d_k^l\bigg\rbrack^+.
$$
The market price function (MPF) of user $i$ is defined as:
% MARKET PRICE 
\begin{align*}
    \tilde{P_i}(z, s_{-i}) &= \displaystyle\sum_{l\in\mcI}P_i^l(z_i^l,
s_{-i}^l)r_i^l \\
    = \displaystyle\sum_{l\in\mcI}&\bigg(\inf\bigg\lbrace y\ge 0 :
\hat{D_i^l}(y,s_{-i}^l)\bigg\rbrace r_i^l\bigg),
\end{align*}
which is interpreted as the aggragate minimum price a user bids over its route in order to obtain the
resource $z$ given the opponents’ profile $s_{−i}$. Its inverse function
$\tilde{D_i}$ is defined as follows:
% INVERSE PRICE (ALLOCATION)
\begin{align*}
    \tilde{D}_i(y, s_{-i}) &= \sup\bigg\lbrace z\in \bigg( 0,
\min_l\hat{D}_i^l/r_i^l\bigg) : \\
    &\tilde{P_i}(z,s_{-i}^l) < y\bigg\rbrace,
\end{align*}
which means the maximum available quantity at a bid price of $y$ given
$s_{−i}^j$. With this notation, the modified PSP allocation rule \cite{tuffin},
\cite{qpsp} is defined
as:
% ALLOCATION RULE
\begin{align*}
    \tilde{a_i}(s) &= \min\big\lbrace d_i^{l(i)}, \\
 &\frac{d_i^{l(i)}}{\sum_{k:p_k^{l(k)}=p_i^{l(i)}}d_k^{l(k)}} \tilde{D_i}(p_i^{l(i)},
s_{-i}^l)\big\rbrace,
\end{align*}
\begin{align*}
    \tilde{c_i}(s) &= \displaystyle\sum_{j\ne i}\bigg\lbrack\sum_{l\in\mcI}
p_j^{l(j)} \bigg(\tilde{a_j}(0; s_{-i}^l)\\
    &-\tilde{a_j}(s_i^l;s_{-i}^l)\bigg) r_i^l\bigg\rbrack,
\end{align*}
 $a_i^{l(i)}$ denotes the quantity user $i$ obtains by a bid price
$p_i^{l(i)}$ (when the
opponents bid $s_{−i}^l$) and the charge to user $i$ by the seller is denoted
$c_i^{l(i)}$. $\sum_{l\in\mcI} c_i^{l(i)}$ is interpreted to be the total cost incurred in the system if
user $i$ is removed from the auction. Note that the allocation rule is modified
from \cite{lazar} according to \cite{tuffin}, so that buyers with identical unit-price
$p_i$ are not rejected.
%%%%%%%%%%%%
\iffalse
An allocation rule is feasible \cite{lazar} if $\forall \ s$,
$$
    \displaystyle\sum_{i\in\mcI} a_i(s) \le Q
$$
and $\forall \ i\in\mcI$,
\begin{align*}
    a_i(s) &\le d_i \\
    c_i(s) &\le p_id_i.
\end{align*}
\fi
%%%%%%%%%%%%%%%%%%

Using this classic PSP mechanism, \cite{lazar} shows that given the opponents bids $s_{-i}$,
user $i$'s $\epsilon$-best response $s_i = (w_i, v_i)$ as a Nash move
(where $s_i$ is chosen to maximize $i$'s utility with $s_{-i}$ held constant), is
given by:
\begin{align}
\begin{split}
    v_i &= \sup\bigg\lbrace d \ge 0 : \theta '(d) > P_i(d), \\ 
&\displaystyle\int_0^d P_i(\eta) \ d\eta \le b_i\bigg\rbrace -
\frac{\epsilon}{\theta_i'(0)} \\
&\qquad\qquad \text{(best quantity reply)} \\
\end{split}\\
    w_i &= \theta_i'(v_i) \quad \text{(best unit-price reply)},
\end{align}
where $\epsilon > 0$ is the bid fee, $b_i$ is user $i$'s budget, and every user
has an elastic demand function.

\subsubsection{Data Allocation using PSP}

The main contribution of this work is to show that the rules of PSP auctions are applicable to the
secondary market described in \cite{zheng}. We find that the auction of data effects the
strategies of the users (buyers and sellers) and results in a (somewhat) different
auction from the original bandwidth problem. We intend to show that our auction
is rational and achieves the desired VCG properties, as does the original
formulation. Using \cite{zheng} as a basis for our model, and \cite{lazar} as
both a theoretic and notational template (BAD SENTENCE), we define optimal strategies for
buyers and sellers which allows for the development of a PSP auction mechanism
to achieve a network equilibrium for cellular data. (EXPAND)

We will introduce a user type called an \emph{opt-out buyer} in order to perform our analysis. The
opt-out buyer restricts its pool of sellers by only submitting bids to sellers
who are able to meet their requirements.
We intend to show that our PSP constraints are
sufficient to attain the desirable property of truthfullness through incentive compatibility. We
reason, due to our pricing mechanism, that our formulation upholds the \emph{exclusion-compensation
principle}, and is a valid progressive second price auction to the extent that buyer $i$
pays for its allocation so as to exactly cover the ``social opportunity cost" which is given by the declared willingness to pay (bids) of the users who are excluded by $i$'s
presence, and thus also compensates the seller for the maximum lost potential
revenue \cite{lazar}.

We extend the P2P rules described in \cite{semret} to include a \emph{local} market
price function as determined by the subset of nodes participating in the
auction, where the seller is its own auctioneer. This implies that the influence of the greater market on the individual
auctions will be influenced only by the submission of bids from buyers to
sellers. As a buyer may have access to multiple auctions, the sellers will be
dynamically influenced by the market via the $\epsilon$-best replies from the
buyers: the
valuation function of seller $j$ is dependent on the buyers demand, and is
modeled as a function of their potential revenue \cite{semret}.

%%%%%%%%%%%%%%%%%%%
\iffalse 
We use the $\alpha$-fair utility functions \cite{zheng} to model the
valuation from consuming $d$ amount of data:
% BUYER VALUATION
\begin{equation}\label{buyervaluation}
    \theta(d) = \frac{\sigma d^{1-\alpha}}{1-\alpha}
\end{equation}
(AUGH! NEED X TO BE SO BIG COMPARED TO ALPHA! can we assume a minimum ask?)
where $\sigma$ is a positive constant representing (the scale) of the usage
utility and we take $\alpha \in [0, 1)$.
We verify that the user valuation above satisfies the conditions for an
\emph{elastic demand function}: (NOTE: this part seems in the wrong place)

\definition{\cite{lazar}}
A real valued function $\theta(\cdot)$ is an \emph{(elastic) valuation
function} on $[0, D]$ if 
\begin{itemize}
    \item $\theta(0) = 0$; \\
        \emph{Verification:} (obvious)
    \item $\theta$ is differentiable; \\
        \emph{Verification:} The derivative, $\sigma d^{-\alpha}$, is positive assuming non-negative
data requirements.
    \item $\theta ' \ge 0$, and $\theta '$ is non-increasing and continuous; \\
        \emph{Verification:} $U$ is differentiable for all $d$, and therefore
continuous. Its derivative is a negative exponential, and so is non-increasing.
    \item There exists $\gamma > 0$, such that for all $z \in [0,D]$, $\theta
'(z) > 0$ implies that for all $\eta \in [0, z), \theta '(z) \le \theta '(\eta)
- \gamma(z - \eta)$. \\
        \emph{Verification:} Without loss of generality, we may set the scaling
constant $\sigma=1$, and compute the curvature $\gamma(\xi)$, where by definition,
$$
    \gamma = \frac{\theta''}{(1+\theta')^{3/2}} = \frac{-\alpha
\xi^{-\alpha-1}}{(1+\xi^{-2\alpha)^{3/2}}}.
$$
Using a Taylor theorem approximation,
\begin{align*}
    z^{-\alpha} &\le \eta^{-\alpha} + \frac{-\alpha
d^{-\alpha-1}}{(1+\xi^{-2\alpha)^{3/2}}}(z-\eta) \\
    & \le \eta^{-\alpha} +
\frac{\alpha}{2\sqrt{2} \xi}(z-\eta)  \\
    &\le \eta^{-\alpha} +
\frac{\alpha}{\xi}(z-\eta).
\end{align*}
Now, using Taylor repeatedly, simplifying and taking the limit as $\eta \rightarrow z$,
\begin{align*}
    z^{-\alpha} - \eta^{-\alpha} &\le -\alpha\eta^{-\alpha-1}(z-\eta) \\
    & \le \frac{-\alpha}{\xi}(z-\eta).
\end{align*}
And so, since $\xi \le \eta^{\alpha+1}$,
we may set
$$
    \gamma \ge
\frac{-\alpha\eta^{-(\alpha+1)^2}}{\big(1+(\eta^{-2\alpha(\alpha+1)})^{3/2}},
$$
which holds in the case that $z > 1$, and so assuming that there must be at least one
unit of data required for a user to have
a valuation,  we have that the concavity of $\theta'$ is shown by Squeeze theorem.
\end{itemize}
\fi
%%%%%%%%%%%%%%%%%%%%%%

@@

We consider the set of $\mcI = \lbrace 1, \cdots, I\rbrace$ users who purchase or sell
data from other users. A buyer submits bids directly to sellers who enough leftover data
to satisfy their demand, and will submit bids in order to maximize their
(private) valuation. We assume (SUPPOSE?) that the public information in the
secondary market consists of a set of offers that are published by users
wishing to sell their data overage. 
A user's identity $i \in \mcI$ as a subscript indicates that the user
is a buyer, and a superscript indicates the seller.
Suppose user $i$ is buying from user $j$. A bid $s_i^j = (d_i^j, p_i^j)$,
meaning $i$ would like to buy from $j$ a quantity $d^j_i$ and is willing to pay
a unit price $p^j_i$. Without loss of generality, we assume that all users bid in all
auctions; if a user $i$ does not submit a bid to $j$, then this means that
the user has the exact amout of data they require, or that seller $j$ does not have
enough data to satisfy the buyers' demand, and we simply set $s_i^j = (0, 0)$.
A seller $j$ places an ask $s^j = (d^j, p^j)$, meaning $j$ is offering a
quantity $d^j$ , with a reserve unit price of $p^j$ . In other words, for a
superscript, the bid is understood as an offer in the secondary
market; we assume that data is a unary resource belonging to the seller, and
therefore can identify the data (for sale) with the identity of the user.
To further clarify this restriction, we note that since $i$ is not a seller,
the superscript notation will not be used, as $d^i = 0$ and
$a^i = 0$. In our current formulation, we do not allow a seller to submit
multiple bids to the secondary market (FUTURE WORK).

Based on the profile of bids $s^j = (s^j_1, \cdots s^j_I)$, seller $j$ computes
an allocation $(a^j, c^j) = A^j(s^j)$, where $a^j_i$ is the quantity given to
user $i$ and $c^j_i$ is the total cost charged to user $i$. $A^j$ is the
allocation rule of seller $j$. It is feasible if $a^j_i \le d_i^j$, and $c^j_i \le  p^j_i d_i^j$.

\section{Distributed PSP Analysis}
\subsection{User Behavior}

\subsubsection{Buyer Strategy}
Absent the cost or revenue from trading data, CMHK users gain utility from consuming
data. 
We will assume that the buyer valuation satisfies the conditions for an
\emph{elastic demand function}: 
\definition{\cite{lazar}}
A real valued function for buyer $i$, $\theta(\cdot)_i$, is an \emph{(elastic) valuation
function} on $[0, b_i]$ if 
\begin{itemize}
    \item $\theta_i(0) = 0$,
    \item $\theta_i$ is differentiable,
    \item ${\theta_i}' \ge 0$, and ${\theta_i}'$ is non-increasing and continuous,
     \item There exists $\gamma > 0$, such that for all $z \in [0,D]$,
${\theta_i}
'(z) > 0$ implies that for all $\eta \in [0, z), {\theta_i}'(z) \le {\theta_i}'(\eta)
- \gamma(z - \eta)$. 
\end{itemize}
% OPT-OUT BUYER
We define a \textbf{opt-out buyer} as a user $i\in\mcI$ with utility
function,
\begin{equation}\label{opt-utility}
    u_i = \theta_i \circ e_i(a) - c_i,
\end{equation}
where $e_i : [0, \infty) \rightarrow [0,\infty)$ is %the expectation 
a function that maps buyer $i$'s data quantity (requirement) to matching
seller(s). We note that the opt-out buyers' valuation depends only on a scalar $e_i(a)$ which is a function of the
quantities of all the available data for sale in the secondary market.

Suppose the total amount of seller $j$'s data on the network at the instance that
user $i$ joins the auction is $b^j$. 
The data transfer from each seller cannot exceed the total amount they have available,
i.e. $a_i^j \le b^j$. This will hold simultaneously for each $i \in
\mcI$ if and only if $b^j \ge \max_i \ a_i^j$. Therefore a seller $j$ is
restricted to subset of buyers $\in\mcI$.
Note that with our formulation, if a seller $j$ does not meet a buyer $i$'s data requirements, a
rational (utility-maximizing) buyer will set $s_i^j = 0$, i.e. they will not
place a bid, as in \cite{zheng}. The seller, in our analysis, is a functional
extension of the buyer, its valuation $\theta^j$ is dependent on the buyers. We will assume that buyers and sellers
are separated (a seller does not also buy data and vice versa).

Although it is possible for a seller to fully satisfy a buyer $i$'s demand, it
is also reasonable to expect that many sellers will come close to using their
entire data cap, and only sell the fractional overage. In this case, we
determine that a buyer must coordinate their bids among multiple sellers. (SAY
MORE?) Buyer $i$'s valuation is interpreted as a unit valuation $\theta_i$,
moderated
by a function of quantities desired from the distributed market. 
We define, in addition to the valuation $\theta_i$ and budget $b_i$, a generic
\textbf{data-provisioning vector} $\vs_i$, held by buyer $i$ as part of its type. We propose the
following strategy,
{
\proposition{(Opt-out buyer strategy)}\label{buyerstrategy}
Define, for any allocation $a$,
% OPT-OUT BUYER STRATEGY
\begin{equation}\label{opt-out}
    %e_i^j(a) \triangleq \frac{a_i^j}{\vs_i^j} + a_j^i,
    e_i^j(a) \triangleq \frac{a_i^j}{\vs_i^j},
\end{equation}
and define,
% MIN SET
$$
    \ell_i =\argmax_{\mcI' \subset \mcI, \vert\mcI'\vert =
n}\sum_{j\in\mcI'} d^j.
$$
Buyer $i$ chooses its seller pool by determining $n$, where
\begin{equation}\label{buyercoordinate}
    n = \argmin_{\ell_i}(j \in \ell_i : \displaystyle\sum_{n} \frac{d^n}{d_i} = d_i\rbrace,
\end{equation} 
which produces the minimal subset 
\begin{equation}\label{sellers}
    \mcI_i = \lbrace j \in \mcI : j < n\rbrace \subset \mcI.
\end{equation} 
Now let $j^* = n < I$, and define, 
\begin{equation}\label{opt-quantity}
    e_i(a) \triangleq e_i^{j^*}(a).
\end{equation}
Then, we have that $e_i$
is an optimal feasible strategy for buyer $i$.
}\\
\textbf{Proof:}
In the case that there exists a seller who can completely satisfy a buyers'
demand, $j^*=1$, $\vert \mcI_i\vert =1$ and (\ref{buyercoordinate}) holds. If such a buyer does not exist,
as the set $\ell_i$ is an ordered set, $i$ may discover 
$j^*$ by computing $\ell_i$. In the case that $d_i >
\sum_{j\in\mcI}d^j/d_i$, then $j^* > I$ and we consider the buyers' demand
infeasible (CAN DO BETTER!). 
We also note that $\mcI_i$ is not the only
possible minimum subset $\in\mcI$ able to satisfy $i$'s demand, it is the minimal subset where a
coordinated bid is possible. We will show optimality through the
analysis in Section \ref{analysis}.

\subsubsection{Buyer Influence}
To determine a strategy for the sellers, we examine seller incentive. The potential revenue for $j$ at unit price $y$ is determined by the
demand of the buyers. $\forall \ y\ge 0$, we determine that the demand is given by,
% BUYER DEMAND 
\begin{equation}\label{datademand}
    \rho^j(y) = \sum_{i\in\mcI : p_i^j\ge y} d_i^j, 
\end{equation}
with ``inverse"
% SELLER REVENUE 
\begin{equation}\label{revenue}
    f^j(z) \triangleq \sup\big\lbrace y\ge 0:
        \rho_i^j(y) \ge z \ \forall \ i \in \mcI\big\rbrace.
\end{equation}
For a given demand $\rho^j$, $f^j$ maps a unit of data to the highest price at
which it \emph{could} be sold to any buyer $i\in \mcI$ (as in \cite{semret}). However, $j$ is restricted by
the bid strategy of the buyers, as well as some natural constraints, and so we have the following Lemma.

{
% SELLER CONSTRAINTS
\lemma{(Seller constraints)}\label{constraints}
Let $j$ be a seller with budget $b^j$.
Formalizing the quantity threshold, the seller must satisfy the quantity
constraint, 
\begin{equation}\label{quantity}
    d^j \ge e_i(a)
\end{equation}
and
\begin{equation}\label{budget}
    \displaystyle\sum_{i\in\mcI} e_i^j(a) \le \sum_{i\in\mcI} d^j_i \le b^j.
\end{equation}
In addition, for a seller who does not sell at a loss, the reserve price must
satisfy 
\begin{equation}\label{reserveprice}
   p^j \ge \min_{i\in\mcI}\big({\theta_i}'(d_i^j)\big).
\end{equation}
Finally, we must have,
\begin{equation}\label{sumallocation}
    \displaystyle\sum_{k\in \mcI, k\ne i} e_k^j(a) \le a_i^j.
\end{equation}
}\\
\textbf{Proof:}
The first statement is an assumption, which we may enforce by (\ref{opt-out}),
and as a seller cannot sell more data than their bid, (\ref{budget}) enforces
the budget constraint for the seller. (\ref{reserveprice})
follows from the assumption that $j$ does not sell at a loss, and finally, (\ref{sumallocation})
follows from Proposition \ref{buyerstrategy}.
